Deep Reinforcement Learning for Conservation Decisions

### 2021-05-12 manuscript/manuscript.Rmd
some references and reworking ethics paragraph (WIP)

>>>>

<!-- second pass at this -->

Algorithms are playing increasingly influential decision-making roles in sectors such as policing, finance, and employment, raising concerns about the ethics, biases, and power entrenched in both the algorithms and their outputs [@kalluri2020]. As algorithms play a greater role in environmental and conservation policy, will similar concerns arise? While this question has garnered  recent interest in the literature [@wearn2019; @adams2019; @scoville2021] the use use of decision making algorithms in environmental applications has largely been confined to the context of classification algorithms (i.e. to identify wildlife poaching [@adams2019] or illegal fishing behavior [@mcdonald2021]). Increasingly, applications of AI to meeting sustainable development goals [@], prioritizing protected area locations [@], and predicting However, good intentions are not sufficient to ensure equitable outcomes. Interdisciplinary collaborations with experts in algorithmic governance and ethics will be important ensure that applications of AI to ecological challenges are applied responsibly.
